Exercise 1.

From STAT 545A MDA project, I found it useful to create a function to compute the range, mean, median, and standard deviation of certain numeric variable across a categorical variable from the dataset.

In addition, the built-in *range()* function can only return a vector, containing the minimum and maximum, which is hard to format into a single output table. For example, using the mtcars dataset:

```{r}
library(tidyverse)
library(testthat)
```

```{r}
head(mtcars)
```

If we try to find the range of mpg across cyl using *group_by()* and *summarize()*, the output table will have duplicated rows, which is not very convenient.

```{r}
example <- mtcars %>%
  group_by(cyl) %>%
  summarize(range = range(mpg))
glimpse(example)
```

Moreover, it is also necessary to write a wrapper for the range() function since it can take \<chr\> as inputs, and it will output the first and last of the characters in alphabetical order. It also regards numeric values as minimum when the input is mixed. For example:

```{r}
example_2 <- c('apple','w','game','o')
example_3 <- c(2, 'apple','w','game','o', 3, 10)
range(example_2)
range(example_3)
```

Therefore, I will create a function addressing the above problems. First I make sure the input 'var' is numeric, while the 'group' variable can be either type. I then convert the output of *range()* to a \<list\>, which is more convenient for further analysis and calculations.

'data' is a data frame (extension); 'group' is a \<chr\> indicating the group variable in the dataset; 'var' is a \<chr\> indicating the numeric variable in the dataset; The output will be a tibble containing the range, mean, median, and standard deviation of 'var' across 'group' in 'data'.

Exercise 2.

```{r}
#' Summary Statistics
#'
#' Compute summary statistics for a numeric variable across a group in a data frame.
#'
#' @param data A data frame.
#' @param group A character indicating the group variable in the dataset.
#' @param var A character indicating the numeric variable in the dataset.
#' @param na.rm Logical, indicating whether to remove missing values (default is TRUE).
#' @param ... Additional arguments to be passed to functions.
#'
#' @return A tibble containing the range, mean, median, and standard deviation of 'var' across 'group' in 'data'.
#'
#' @examples
#' summary_statistics(iris, "Species", "Sepal.Length")
#'
#' @export
summary_statistics <- function(data, group, var, na.rm = TRUE, ...) {
  # Check if input variable is numeric
  var_name <- as.character(substitute(var))
  if (!is.numeric(data[[var_name]])) {
    stop("Variable '", var_name, "' is not numeric in the data.")
  }
  
  #Summary statistics
  data %>%
    group_by({{group}}) %>%
    summarise(
              'range' = list(range({{var}})), 
              'mean' = mean({{var}}),
              'median' = median({{var}}),
              'std' = sd({{var}})
    )
}

```

Exercise 3.

The built-in dataset 'iris' is first used to demonstrate the usage of this function. Notice that the dataset needn't to be a tibble.

```{r}
head(iris)
```

If we want to see the sepal length according to species, we can apply the function:

```{r}
glimpse(summary_statistics(iris, Species, Sepal.Length))
```

However, if 'var' is not numeric, the function will report error:

```{r error=TRUE}
glimpse(summary_statistics(iris, Sepal.Length, Species))
```

Moreover, 'group' can also be a numeric variable. We use 'mtcars' this time to see the mpg according to number of gears:

```{r}
glimpse(summary_statistics(mtcars, gear, mpg))
```

Exercise 4.

In this exercise I will make two special data frames to test the function.

Vector with no NA: 1) test if variable names are correct; 2) test if number of groups are correct, 3) test if range is a list type.

```{r}
test_that("Test 1: Vector with no NA", {
  # create a random tibble with no NA
  data <- tibble(
    group = c(1,3,4,6,'chr',3,5,6,'chr',2),
    value = c(3.14, 0.98, 7.25, 2.67, 5.42, 1.23, 8.56, 4.79, 6.33, 9.01)
  )
  # apply the function
  result <- summary_statistics(data, group, value, na.rm = TRUE)

  # test if variable names are correct; test if number of groups are correct, test if range is a list type
  expect_true(all(c('group','range','mean','median','std') %in% colnames(result)))
  expect_length(result$group, 7)
  expect_type(result$range, 'list')
  
})
```

2.  Vector of a different type: 4) test if error occurs when var contains \<chr\>.

```{r}
test_that("Test 2: Vector of a different type", {
  
  # create a random tibble with no NA and var contains <chr>
  data <- tibble(
    group = c(1,3,4,6,4,3,5,6,7,2),
    value = c(3,44,5,'a','b','c','d',3,6,1)
  )
  
  # test if error occurs
  
  expect_error(summary_statistics(data, group, value, na.rm = TRUE))
  
})
```
